Model Samples Processing

### 2020-02-09 stats/model_sample_processing.Rmd
new model run no random effects

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)

@@

model <- bind_rows(
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
)

@@

```{r}
model_pred <- model %>%
  filter(a == "modelPrediction")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred, "../saves/model_pred_re.rds")

```{r}
item_params <-  model %>%
  filter(b == "items")%>%
  select(-a,-b, -e, -f, -h)%>%
    rename(item = c,
         parameter = d,
         value = g)

saveRDS(item_params, "../saves/item_params_re.rds")

saveRDS(global_params, "../saves/global_params_re.rds")

saveRDS(item_sigma, "../saves/item_sigma_re.rds")

subject_sigma<- model %>%
  filter(b == "sigma", 
         c != "global_sem_sigmas")%>%
  select(-a,-b, -e,-f,-h, -d)%>%
    rename(parameter = c,
         value = g)

saveRDS(subject_sigma, "../saves/subject_sigma_re.rds")
```

>>>>

```{r}
library(tidyverse)
#library(rwebppl)
#library(brms)
#library(coda)
#library(ggthemes)
library(readxl)
#library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
#library(bigmemory)

@@

model <- bind_rows(
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
)

item_params <-  model %>%
  filter(b == "items")%>%
  select(-a,-b, -e, -f, -h)%>%
    rename(item = c,
         parameter = d,
         value = g)

saveRDS(item_params, "../saves/item_params_2.rds")

saveRDS(global_params, "../saves/global_params_2.rds")

saveRDS(item_sigma, "../saves/item_sigma_2.rds")

#subject_sigma<- model %>%
#  filter(b == "sigma", 
#         c != "global_sem_sigmas")%>%
#  select(-a,-b, -e,-f,-h, -d)%>%
#    rename(parameter = c,
#         value = g)

#saveRDS(subject_sigma, "../saves/subject_sigma.rds")

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "pragmatic")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prag, "../saves/model_pred_prag_2.rds")

model_pred <- model %>%
  filter(a == "modelPrediction",
         b == "global")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred, "../saves/model_pred_global_2.rds")

model_pred_flat <- model %>%
  filter(a == "modelPrediction",
         b == "flat")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_flat, "../saves/model_pred_flat_2.rds")

model_pred_prior <- model %>%
  filter(a == "modelPrediction",
         b == "prior")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prior, "../saves/model_pred_prior_2.rds")

@@

```{r}
bind_rows(
  readRDS("../saves/item_params_1.rds"),
  readRDS("../saves/item_params_2.rds")
)%>%
  saveRDS(., "../saves/item_params.rds")

bind_rows(
  readRDS("../saves/global_params_1.rds"),
  readRDS("../saves/global_params_2.rds")
)%>%
  saveRDS(., "../saves/global_params.rds")

bind_rows(
  readRDS("../saves/item_sigma_1.rds"),
  readRDS("../saves/item_sigma_2.rds")
)%>%
  saveRDS(., "../saves/item_sigma.rds")

bind_rows(
  readRDS("../saves/model_pred_prag_1.rds"),
  readRDS("../saves/model_pred_prag_2.rds")
)%>%
  saveRDS(., "../saves/model_pred_prag.rds")

bind_rows(
  readRDS("../saves/model_pred_global_1.rds"),
  readRDS("../saves/model_pred_global_2.rds")
)%>%
  saveRDS(., "../saves/model_pred_global.rds")

bind_rows(
  readRDS("../saves/model_pred_flat_1.rds"),
  readRDS("../saves/model_pred_flat_2.rds")
)%>%
  saveRDS(., "../saves/model_pred_flat.rds")

bind_rows(
  readRDS("../saves/model_pred_prior_1.rds"),
  readRDS("../saves/model_pred_prior_2.rds")
)%>%
  saveRDS(., "../saves/model_pred_prior.rds")
```
